How Kids Code and How We Know:\\An Exploratory Study on the Scratch Repository

### 2016-04-22 Paper/paper.tex
Removed indentation metrics

\begin{table*}[ht]
	\centering
	\begin{tabular}{lrrrrrr}
		\hline
		&\textbf{mean}&\textbf{min}&\textbf{Q1}&\textbf{median}&\textbf{Q3}&\textbf{max}\\
		\hline
		Sprites with code per project&5.68&1&1&2&5&525\\
		Scripts per project&17.35&1&2&5&12&3038\\
		Maximum indentation per project&4.56&1&3&3&5&488\\
		Lines of code (LOC) per project&154.55&1&12&29&76&34622\\
		LOC in Stage per project&4.80&0&0&0&3&2613\\
		LOC in Sprites per project&115.57&0&10&26&68&34613\\
		LOC in Procedures per project&34.17&0&0&0&0&20552\\
		McCabe Cyclomatic Complexity (CC) per script&1.58&1&1&1&1&246\\
		McCabe CC per procedure script&3.75&1&1&2&4&183\\
		Procedures per project with procedures&11.50&1&1&2&6&847\\
		Arguments per Procedure&0.95&0&0&0&1&53\\
		Numerical arguments per procedure with arguments&1.73&0&1&1&2&22\\
		Text arguments per procedure with arguments&0.28&0&0&0&1&24\\
		Boolean arguments per procedure with arguments&0.13&0&0&0&0&14\\
		Calls per procedure&2.14&0&1&1&2&526\\
		Scripts with calls per procedure&1.13&0&1&1&1&59\\
		Variables per project&2.06&0&0&0&1&340\\
		Scripts utilizing variable&4.97&1&1&3&5&1127\\
		Lists per project&0.55&0&0&0&0&319\\
		Conditional statements per project&10.02&0&0&0&3&5950\\
		Recursive loop statements per project&7.65&0&1&2&5&2503\\
		User input blocks per project&4.77&0&0&1&4&1889\\
		Broadcast-receive statements per project&8.57&0&0&0&2&2460\\	
		\hline
	\end{tabular}
	\caption{Summary statistics from the dataset of \nScriptPrograms~non-empty Scratch projects}
	\label{tbl-size}
\end{table*}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.45\textwidth]{fig/charts/1sprites}
	\caption{Histogram of the number of sprites in the analyzed projects}
	\label{fig:size-sprites}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.45\textwidth]{fig/charts/1scripts}
	\caption{Histogram of the number of scripts in the analyzed projects}
	\label{fig:size-scripts}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.45\textwidth]{fig/charts/1locs}
	\caption{Histogram of the lines of code in the analyzed projects}
	\label{fig:size-locs}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.45\textwidth]{fig/charts/1indent}
	\caption{Histogram of the maximum code indentation level in the analyzed projects}
	\label{fig:size-indent}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.45\textwidth]{fig/charts/3cyclomatic}
	\caption{Histogram of the McCabe cyclomatic complexity of the \nscripts~analyzed scripts}
	\label{fig:cyclomatic}
\end{figure}

In Table \ref{tbl-size} we summarize statistics for metrics related to size and complexity. We use the mean value and the five-number summary to describe the dataset in terms of the number of sprites with code per project (including the stage sprite) and the number of scripts per project. We furthermore measure the lines of code per project, considering each Scratch block to represent exactly one line of code, thus not counting the closing constructs of loops or conditional statements as separate lines. Figures \ref{fig:size-sprites}, \ref{fig:size-scripts}, \ref{fig:size-locs} and \ref{fig:size-indent} plot the distribution of these size metrics.

>>>>

\begin{table*}[ht]
	\centering
	\begin{tabular}{lrrrrrr}
		\hline
		&\textbf{mean}&\textbf{min}&\textbf{Q1}&\textbf{median}&\textbf{Q3}&\textbf{max}\\
		\hline
		Sprites with code per project&5.68&1&1&2&5&525\\
		Scripts per project&17.35&1&2&5&12&3038\\
		Lines of code (LOC) per project&154.55&1&12&29&76&34622\\
		LOC in Stage per project&4.80&0&0&0&3&2613\\
		LOC in Sprites per project&115.57&0&10&26&68&34613\\
		LOC in Procedures per project&34.17&0&0&0&0&20552\\
		McCabe Cyclomatic Complexity (CC) per script&1.58&1&1&1&1&246\\
		McCabe CC per procedure script&3.75&1&1&2&4&183\\
		Procedures per project with procedures&11.50&1&1&2&6&847\\
		Arguments per Procedure&0.95&0&0&0&1&53\\
		Numerical arguments per procedure with arguments&1.73&0&1&1&2&22\\
		Text arguments per procedure with arguments&0.28&0&0&0&1&24\\
		Boolean arguments per procedure with arguments&0.13&0&0&0&0&14\\
		Calls per procedure&2.14&0&1&1&2&526\\
		Scripts with calls per procedure&1.13&0&1&1&1&59\\
		Variables per project&2.06&0&0&0&1&340\\
		Scripts utilizing variable&4.97&1&1&3&5&1127\\
		Lists per project&0.55&0&0&0&0&319\\
		Conditional statements per project&10.02&0&0&0&3&5950\\
		Recursive loop statements per project&7.65&0&1&2&5&2503\\
		User input blocks per project&4.77&0&0&1&4&1889\\
		Broadcast-receive statements per project&8.57&0&0&0&2&2460\\	
		\hline
	\end{tabular}
	\caption{Summary statistics from the dataset of \nScriptPrograms~non-empty Scratch projects}
	\label{tbl-size}
\end{table*}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.45\textwidth]{fig/charts/1sprites}
	\caption{Histogram of the number of sprites in the analyzed projects}
	\label{fig:size-sprites}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.45\textwidth]{fig/charts/1scripts}
	\caption{Histogram of the number of scripts in the analyzed projects}
	\label{fig:size-scripts}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.45\textwidth]{fig/charts/1locs}
	\caption{Histogram of the lines of code in the analyzed projects}
	\label{fig:size-locs}
\end{figure}
\begin{figure}
	\centering
	\includegraphics[width=0.45\textwidth]{fig/charts/3cyclomatic}
	\caption{Histogram of the McCabe cyclomatic complexity of the \nscripts~analyzed scripts}
	\label{fig:cyclomatic}
\end{figure}

In Table \ref{tbl-size} we summarize statistics for metrics related to size and complexity. We use the mean value and the five-number summary to describe the dataset in terms of the number of sprites with code per project (including the stage sprite) and the number of scripts per project. We furthermore measure the lines of code per project, considering each Scratch block to represent exactly one line of code, thus not counting the closing constructs of loops or conditional statements as separate lines. Figures \ref{fig:size-sprites}, \ref{fig:size-scripts}, \ref{fig:size-locs} and plot the distribution of these size metrics.
